\documentclass[11pt,a4paper,twoside]{article}
\usepackage[latin9]{inputenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{color}
\usepackage{ifthen}
%\usepackage{fdsymbol}
\usepackage{tikz}
%\usepackage{revsymb}
\usepackage{amsfonts}
\usepackage{amsthm}

\makeatletter

\pagenumbering{arabic}


\setlength{\oddsidemargin}{0.3cm}
\setlength{\evensidemargin}{0.3cm}
\setlength{\textwidth}{15.9cm}

\newcommand{\checkedSquare}{\mbox{\ooalign{$\checkmark$\cr\hidewidth$\square$\hidewidth\cr}}}
\newcommand{\soln}[1]
{
\ifthenelse{\equal{\solutions}{1}}{ \textcolor[RGB]{40, 60, 250}{#1}}{}
}
\newcommand{\qu}[1]
{
\ifthenelse{\equal{\solutions}{0}}{#1}{}
}
\newcommand{\anticomm}[2]{\{#1,#2\}}

\renewcommand{\labelenumi}{(\alph{enumi})}


\makeatother

\def \solutions{0}

\begin{document}
\vspace*{-3cm}
TN3125: Information and Computation 2019-20 \hspace*{2cm}{September $11^{\mathrm{th}}$, 2019}\\

\vspace{8cm}

\noindent \begin{center}
\textbf{{\Large Minitest 1}}\\
\par\end{center}

\vspace*{1cm}

\noindent \textbf{Important notes:}

\begin{itemize}
\item This exam is CLOSED book.
\item The use of phones is not permitted. Please leave your phone by the examiner if you must go to the bathroom during the exam.
\item Please clearly write your name and fill in your student ID by shading the appropriate entries on the grid above.
\item Please write your answers on the white space below the question. 
\item Please show as much of your work as possible; this includes explaining the reasoning behind your calculations, we really like to give partial credit.
\item All problems can be solved without lengthy computations. We advise you to look for a simple solution if you can.
\item This exam has {\bf 2 problems} (100 points total) on {\bf XX pages}, including this one.
\end{itemize}
\vspace{2cm}
Good luck!



\newpage
\noindent \textbf{Problem 1:} \emph{Measuring information} (50 points total)\\
Let us imagine that you want to transmit a word from the foreign language Icish to a friend. 
In this language words have always only two letters, first a consonant then a vowel. 
The consonants in the language are $\mathcal C=\{b,c,d,f\}$ and they occur respectively with probabilities $\{1/2,1/4,1/4,0\}$. 
The vowels in the language are $\mathcal V=\{a,e,i,o,u\}$. The probability of having a vowel in a word depends on the consonant as follows:

\[
\begin{array}{c|c|c|c|c|c}  & a & e & i& o &u\\\hline b & 1/2 &1/4 &1/4 & &\\\hline c &  &1/2 &1/4 &1/4 &\\\hline d &1/4  & &1/2 &1/4 &\\\hline f &1/4  &1/4 & &1/2 &\end{array}
\]
\begin{enumerate}
\item What is the entropy of $C$? (5 points) %more precise

\noindent\fbox{
  \parbox{.9\textwidth}{
Answer 1a\hfill
    \vspace{6cm}
  }
}

\item What is the entropy of $V$? (5 points) 

\noindent\fbox{
  \parbox{.9\textwidth}{
Answer 1b\hfill
    \vspace{6cm}
  }
}

\item What is the entropy of a vowel given that the consonant was $b$? (5 points) 

\noindent\fbox{
  \parbox{.9\textwidth}{
Answer 1c\hfill
    \vspace{6cm}
  }
}

\item What is the entropy of a word? (15 points) 

\noindent\fbox{
  \parbox{.9\textwidth}{
Answer 1d\hfill
    \vspace{12cm}
  }
}

\item Construct a Huffman code to transmit words (20 points)

\noindent\fbox{
  \parbox{.9\textwidth}{
Answer 1e\hfill
    \vspace{19cm}
  }
}

\end{enumerate}
\newpage
\noindent \textbf{Problem 2:} \emph{} (50 points total)\\
\end{document}
