\documentclass[11pt,a4paper,twoside]{article}
\usepackage[latin9]{inputenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{color}
\usepackage{ifthen}
%\usepackage{fdsymbol}
\usepackage{tikz}
%\usepackage{revsymb}
\usepackage{amsfonts}
\usepackage{amsthm}

\makeatletter

\pagenumbering{arabic}


\setlength{\oddsidemargin}{0.3cm}
\setlength{\evensidemargin}{0.3cm}
\setlength{\textwidth}{15.9cm}

\newcommand{\checkedSquare}{\mbox{\ooalign{$\checkmark$\cr\hidewidth$\square$\hidewidth\cr}}}
\newcommand{\soln}[1]
{
\ifthenelse{\equal{\solutions}{1}}{ \textcolor[RGB]{40, 60, 250}{#1}}{}
}
\newcommand{\qu}[1]
{
\ifthenelse{\equal{\solutions}{0}}{#1}{}
}
\newcommand{\anticomm}[2]{\{#1,#2\}}

\renewcommand{\labelenumi}{(\alph{enumi})}


\makeatother

\def \solutions{0}

\begin{document}
\vspace*{-3cm}
TN3125: Information and Computation 2019-20 \hspace*{2cm}{September $18^{\mathrm{th}}$, 2019}\\

\vspace{8cm}

\noindent \begin{center}
\textbf{{\Large Minitest 2}}\\
\par\end{center}

\vspace*{1cm}

\noindent \textbf{Important notes:}

\begin{itemize}
\item This exam is CLOSED book.
\item The use of phones is not permitted. Please leave your phone by the examiner if you must go to the bathroom during the exam.
\item Please clearly write your name and fill in your student ID by shading the appropriate entries on the grid above.
\item Please write your answers on the white space below the question. 
\item Please show as much of your work as possible; this includes explaining the reasoning behind your calculations, we really like to give partial credit.
\item All problems can be solved without lengthy computations. We advise you to look for a simple solution if you can.
\item This exam has {\bf 2 problems} (100 points total) on {\bf XX pages}, including this one.
\end{itemize}
\vspace{2cm}
Good luck!



\newpage
\noindent \textbf{Problem 1:} \emph{Compressing a run} (50 points total)\\
Let $X$ be an ensemble with probabilities $\{1/2,1/4,1/8,1/8\}$. 
\begin{enumerate}
\item (10 points) Indicate which of the following set of codes are instantaneous and which are uniquely decodable:
\begin{itemize}
\item $C_1=\{00,01,10,11\}$
\item $C_2=\{0,00,1,10\}$
\item $C_3=\{\}$
\item $C_4=\{0,00,1,10\}$
\end{itemize}
\item (10 points) Construct the Huffman code for this ensemble and give its average length
\item (10 points) Construct the Shannon code for this ensemble and give its average length
\item (10 points) What can we deduce about the entropy of $X$ from the average lengths of the Huffman and Shannon codes?
\item (10 points) Let us use $Y$ the first intermediate ensemble in the Huffman construction to estimate $X$. Let us call $X'$ the estimate. Give a bound on the entropy of $H(X|Y)$ as a function of the error in the estimation (Hint: you can use Fano's inequality).
\item (10 points, bonus) Let us consider the opposite goal to our previous efforts. Suppose that you want to transform a sequence of uniform binary random variables $X_1,X_2,\ldots$ into some random variable $Y$:
\begin{itemize}
\item Describe a general procedure that allows to produce samples of $Y$ from outcomes of uniform binary random variables.
\item Bound the average number of samples necessary to produce a sample of $Y$ is $Y$ is a binary random variable with probabilities $\{p,1-p\}.$
\end{itemize}
\end{enumerate}


\newpage
\noindent \textbf{Problem 2:} \emph{} (50 points total)\\
\end{document}
